\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2023-02-27 paper/main.tex
finish introduction

The above two assumptions create a curious inconsistency; a player with a finite
memory in the game stage can recall infinite information regarding their
interactions and each interaction's outcomes in the update stage. Previous work
has explored the effects of constraining the interactions an individual has.
This can be done by letting individuals have a stochastic number of
interactions~\cite{roca:PhysicalReview:2006, sanchez:JTB:2005,
Traulsen:JTB:2007}, a small number of interactions, or even in the extreme case
a single interaction~\cite{Woelfing:JTB:2009}. However, no previous work
considers that not only the interactions are limited but also the information
regarding each interaction. To this end, we propose a framework in which
individuals, similar to the decisions at each turn, estimate their fitness based
on a minimum of information.

We first consider two extreme scenarios, the classical scenario where an individual
has a perfect memory of all their interactions and the alternative scenario of
limited memory where individuals update their strategies only based on the very
last payoff they obtained. We demonstrate the effects of limited updating payoff
memory using a pairwise comparison process and the well studied game of the
prisoner's dilemma. We observe that individuals with limited memory tend to
adopt less generous strategies and they achieve less cooperation when
interacting in a prisoner's dilemma. We obtain similar results when we consider
that individuals update their strategies based on more information. More
specifically, up to the last two payoffs they obtained when interacting with up
to two different members of the population.

>>>>

The above two assumptions create a curious inconsistency; a player with a finite
memory in the game stage can recall infinite information regarding their
interactions and each interaction's outcomes in the update stage. Previous work
has explored the effects of constraining the interactions an individual has.
Either by letting individuals have a stochastic number of
interactions~\cite{roca:PhysicalReview:2006, sanchez:JTB:2005,
Traulsen:JTB:2007} or by only allowing for
a single interaction~\cite{Woelfing:JTB:2009}. However, no previous work
considers that not only the interactions are limited but also the information
regarding each interaction. To this end, we propose a framework in which
individuals, similar to the decisions at each turn, estimate their fitness based
on a minimum of information.

We first consider two extreme scenarios, the classical scenario where an individual
has a perfect memory of all their interactions and the alternative scenario of
limited memory where individuals update their strategies only based on the very
last payoff they obtained. We demonstrate the effects of limited payoff
memory using a pairwise comparison process and the well studied game of the
prisoner's dilemma. We observe that individuals with limited payoff memory tend to
adopt less generous strategies and they achieve less cooperation when
interacting in a prisoner's dilemma. We obtain similar results when we consider
that individuals update their strategies based on more information. More
specifically, up to the last two payoffs they obtained when interacting with up
to two different members of the population.
